A Formal Model of Checked C

### 2023-01-20 sandp23/evaluation.tex
update.

\subsection{Dataset}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
The~\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

%\input{figures/memoryoverhead}
\Cref{fig:runtimeoverhead} shows the overhead of the partitioned programs.
%It is interesting to see a lot of variance in the runtime overhead.
The runtime overhead is proportional to the execution time 
spent in the sandbox and the number of transitions between~\cregion and the sandbox,
which coincides with the sandbox execution overhead observation in the micro-benchmarks experiments (\Cref{fig:microbenchmarks}).
\Cref{table:conversioneffort} shows the numbers of lines in the sandbox for our partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers without code in the sandbox and transitions to/from the sandbox.
Consequently, the overhead is less than 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we sandboxed only request handlers (relatively small)
that parse messages and return the actions that need to be performed.
The server only invokes these handlers on particular requests resulting in less transitions with the sandbox.
As expected, the overhead is also less in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is high because of the relatively large amount of code in sandbox region.
In both applications, we place the frequently used parsing functions in the sandbox 
resulting in a lot of sandbox transitions with most of them in a loop.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm},
where we made the entire~\code{png} structure tainted, 
which resulted in dynamic checks every time when the~\code{png} struct is accessed.
In summary, our results indicate that the runtime overhead largely depends on the sandbox.

@@

The~\fig{XXX} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.
\aravind{Arun, we should do this experiment. This should be fairly easy.}

>>>>

\subsection{Dataset}
Network-facing programs such as servers directly interact with external input, often process complex data types, and are more susceptible to security issues.
We primarily focus on network servers as they can benefit most from our partitioning approach.
We use WebAssembly (WASM) as our target sandbox. Consequently, we also want any of the selected programs to be compilable with the WASM sandbox.
We selected network servers that we could (with minimal effort) compile with the WASM compiler.
We also selected a few standalone programs suggested by the ~\checkedc team~\cite{benchmarkcc}, which are good candidates to evaluate modifications to~\checkedc.
\tbl{table:dataset} shows the program selected as part of our evaluation dataset.

@@

%\input{figures/memoryoverhead}
The first set of bars in~\Cref{fig:runtimeoverhead} shows the overhead of the partitioned programs.
%It is interesting to see a lot of variance in the runtime overhead.
The runtime overhead is proportional to the execution time 
spent in the sandbox and the number of transitions between~\cregion and the sandbox,
which coincides with the sandbox execution overhead observation in the micro-benchmarks experiments (\Cref{fig:microbenchmarks}).
\Cref{table:conversioneffort} shows the numbers of lines in the sandbox for our partitioned programs.
For~\texttt{ProFTPD}, we used only tainted pointers without code in the sandbox and transitions to/from the sandbox.
Consequently, the overhead is less than 4.2\%.
For~\texttt{UFTPD} and~\texttt{MicroHTTPD}, we sandboxed only request handlers (relatively small)
that parse messages and return the actions that need to be performed.
The server only invokes these handlers on particular requests resulting in less transitions with the sandbox.
As expected, the overhead is also less in these cases.
For~\texttt{TinyBigNum} and~\texttt{Parsons}, the overhead is high because of the relatively large amount of code in sandbox region.
In both applications, we place the frequently used parsing functions in the sandbox 
resulting in a lot of sandbox transitions with most of them in a loop.
The case is slightly different in~\texttt{pnm2png} and~\texttt{png2pnm},
where we made the entire~\code{png} structure tainted, 
which resulted in dynamic checks every time when the~\code{png} struct is accessed.
In summary, our results indicate that the runtime overhead largely depends on the sandbox.

@@

The second set of bars in~\fig{fig:runtimeoverhead} shows the runtime overhead. The overhead is negligible in all cases.
This shows that~\systemname{} fundamentally has the least overhead.
%\aravind{Arun, we should do this experiment. This should be fairly easy.}
